Supplementary figures

### 2021-06-29 code/figure6.Rmd
Update fig5 and 6 with new model. Fix knit error with figure 3

## Getting n_race for white and black
cancerinfo <- read_csv("../data/survival/clinical_plus_cluster.csv")
cancer.clusttype <- cancerinfo %>% dplyr::select(type, race, clust_knn) %>% ## select relevant columns
  filter(race %in% c("WHITE", "BLACK OR AFRICAN AMERICAN")) ## filter black and white only
cancer.race <- as.data.frame(table(cancer.clusttype$type)) ## table cancer type
cancer.race$facetname <- paste0(cancer.race$Var1, " (N = ", cancer.race$Freq, (")")) ## Create a new col with type and freq together
cancer.race$Freq <- NULL ## Remove Freq Column
names(cancer.race) <- c("tiss", "facetname") ## rename cols for left join in kclassplot below

@@

## Processing data
kclnames = grep("k\\[",names(dfsamps), value=TRUE)
dfclas = dfsamps[,kclnames]
dfclas = stack(dfclas)
names(dfclas) = c("value","coefname")
dfclas$class = as.factor(as.numeric(gsub("k\\[(.*),(.*)\\]","\\2",dfclas$coefname)))
dfclas$tiss = tisnames[as.numeric(gsub("k\\[(.*),(.*)\\]","\\1",dfclas$coefname))]
dfclas$class <- fct_rev(dfclas$class)

## Left joining data created above
dfclas <- left_join(dfclas, cancer.race, by = "tiss") ## add facet names

@@

	## Plotting
	ggplot(dfclas,aes_(x = quote(value),y = quote(class), fill = quote(class))) + geom_density_ridges(alpha = alpha.setup) +
		facet_wrap(. ~ facetname,nrow=3) + theme_minimal() + scale_fill_brewer(palette = "Paired") +
		xlim(0,3) + theme(legend.position = "none") + ggtitle("Class Specific Coefficients") +
	  labs(x = expression(paste("k"["cl"])), y = "Cluster Identity") +
	  #geom_text(data = dfclas, aes(label = lab), x = 2.5, y = 6) +
	  mytheme + theme(plot.title= element_text(hjust = 0.5))+ turn.off.legend +
	  scale_fill_manual(values = cluster.colours)
```

>>>>

## Getting n_race for white and black
cancerinfo <- read_csv("../data/survival/clinical_plus_cluster.csv")
cancer.clusttype <- cancerinfo %>% dplyr::select(type, race, clust_knn) ## select relevant columns
n_cancer <- as.data.frame(table(cancer.clusttype$type)) ## table cancer type
n_cancer$facetname <- paste0(n_cancer$Var1, " (N = ", n_cancer$Freq, (")")) ## Create a new col with type and freq together
n_cancer$Freq <- NULL ## Remove Freq Column
names(n_cancer) <- c("tiss", "facetname") ## rename cols for left join in kclassplot below

@@

## Processing data
load("../data/survival/survmodel_effcl_knn_062521.stansave")
dfsamps <- as.data.frame(samps)
clnames = grep("effage0\\[",names(dfsamps), value=TRUE)
dfclas = dfsamps[,clnames]
dfclas = stack(dfclas)
names(dfclas) = c("value","coefname")
dfclas$class = as.factor(as.numeric(gsub("effage0\\[(.*),(.*)\\]","\\2",dfclas$coefname)))
dfclas$tiss = tisnames[as.numeric(gsub("effage0\\[(.*),(.*)\\]","\\1",dfclas$coefname))]
dfclas$class <- fct_rev(dfclas$class)

## Left joining data created above
dfclas <- left_join(dfclas, n_cancer, by = "tiss") ## add facet names

@@

normal_lines <- data.frame(facetname = unique(dfclas$facetname),
                         x0 = 1) ## Add dashed line at x = 1

	## Plotting
	ggplot(dfclas,aes_(x = quote(value),y = quote(class), fill = quote(class))) + geom_density_ridges(alpha = alpha.setup) +
		facet_wrap(. ~ facetname,nrow=3) + theme_minimal() + scale_fill_brewer(palette = "Paired") +
	  theme(legend.position = "none") + ggtitle("Class Specific Coefficients") +
	  labs(x = expression(paste("A"["cl"])), y = "Cluster Identity") +
	  theme(plot.title= element_text(hjust = 0.5)) +
	  scale_fill_manual(values = cluster.colours) +
	  scale_x_continuous(breaks=seq(0.5,1.5, by = 0.5), limits = c(0.5,1.5)) +
    geom_vline(aes(xintercept=1), linetype = "dashed", color = "red")
```
